---
title: "Segmentation function"
author: "Felipe Barros (f.barros@iis-rio.org)"
date: "8 de março de 2016"
output: pdf_document
---

A segmentação de imagens visa agrupar pixels com características similares, como por exemplo, nível de cinza, textura e contraste, resultando em áreas com unidades homogêneas. Logo, a segmentação baseia-se em análise estatística espacial por crescimento de regiões, onde tem-se como parâmetros a quantidade mínima de pixel (para criar a região) e um limiar de similaridade (*threshold* usado apra definir quão similar determinado pixel é em relação aos pixels vizinhos). Assim, pode-se dizer que a segmentação diferencia áreas homogêneas com padrões diferentes aos seus vizinhos, criando $n$ regiões diferentes na imagem. porém tal abordagem não classifica as regioes criadas quanto ao pertencimento a um mesmo grupo ou não. Para mais informações sobre segmentação, [ver manual *spring*](http://www.mundogeomatica.com.br/Livros/Livro_Spring_5.1.2_Aplicacoes_Praticas/LivroSPRING512PassoaPassoAplicacaoPratica.pdf), íten 7.7, página 127.

A abordagem aqui apresentada, **não está baseada no método de crescimento por região**. Mas cria $n$ grupos com áreas homogêneas, a partir dos valores dos pixels da(s) imagem(ns). Portanto, não consideram elementos como, contraste e textura. Em resumo, esta abordagem classifica da imagem em $n$ grupos (definidos pelo usário), que serão classificados estatísticamente através da análise de cluster (K-means) e posteriormente *extrapolado* (usado para classificação) para toda a imagem em questão.

```{r}
source('segmentation.R')
args(segmentation)
```  
  
##Function arguments: 
1. **envLayer**: raster object;
1. **studyArea**: sptail polygon;
1. **projName**: a sufix to be used on output names;
1. **randomForest**: TRUE/FALSE - if the segmentation must be run with randomForest or not;
1. **random.pt**: number of random points to be generated **if** using randomForest classification. IF **NULL**, the function will generate **0.01*ncell(envLayer)** (1% of envLayer's cells) random points.
1. **Kmeans**:  TRUE/FALSE - if the segmentation must be run with Kmeans analysis or not;
1. **ngroup**: number of classes to be identifyed. If **NULL**, and running randomForest algorithm, the function will plot the Kmeans variance analysis and ask the number of groups wanted. Thus the decision can be done based on the plot.
1. **polygonize**: TRUE/FALSE - whether or not to the segmentation must be saved **also** in *shapefile* format;
  
```{r, echo=TRUE, message=FALSE, warning=FALSE}
# loading libraries
library(rgdal)
library(raster)
library(rgeos)
library(RColorBrewer)
```
```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
MT_prec <- stack('./raster/MT_prec.tif')

#Loading MT state limit
MT <- readOGR(dsn = './shp', layer = 'MT')
```  
#Input data:

## Raster Layer

A raster Environmental data (or any other spatial variables with continous values).
Can be a single raster layer or raster stack.

```{r}
# Data set:
plot(MT_prec[[1]], main='Environmental dataset')
```  

##Vector layer

A study area in polygon format.

```{r}
plot(MT, main='Study area', axes=TRUE)
```
  
# Segmentation algorithms:
The segmentation function is implemented to run with two algorithms:
1. The function can be run interely with Kmeans cluster analysis;
**or/and** 
1. with randomForest classification after Kmeans group identification.

In any case, the Kmeans is used to identify $n$ classes (clusters) from the data provided.
For more information about [Kmeans](https://en.wikipedia.org/wiki/K-means_clustering).  

##Running the segmentation with randomForest
  
```{r, warning=FALSE}
  segmentation(envLayer = MT_prec, #raster Layer or raster stack
    studyArea = MT, # SpatialPolygonsDataFrame
    randomforest = TRUE,
    projName = 'MT_yr_prec',
    random.pt = NULL, # Number of random points to be genarated to run randomForest
    Kmeans = FALSE,
    ngroup = 6, # Number of classes to be classified
    polygonize = FALSE)
```  

By randomForest, a random points is generated in the study area from which the values will be analysed with Kmeans analysis and the *k* groups (**clusters**) will be created. After that, the pixel values and its group assotiated with be used as a train set to run randomForest classification.


##Running the segmentation with Kmeans
 
**The Kmeans cluster analysis and randomForest classification will use all raster layers in the analysis**
  
```{r, warning=FALSE}
segmentation(envLayer = MT_prec, #raster Layer or raster stack
  studyArea = MT, # SpatialPolygonsDataFrame
  randomforest = FALSE,
  projName = 'MT_yr_prec',
  random.pt = NULL, # Number of random points to be genarated to run randomForest
  Kmeans = TRUE,
  ngroup = 6, # Number of classes to be classified
  polygonize = FALSE)
```
When running the segmentations interely with Kmeans, **all the pixels values from all raster layers are used to run the Kmeans cluster analysis**. After that, the pixels values are swiched to the group value.
  
###Comparing results from both methods
```{r}
rf_result <- raster('./rf_segmentation_MT_yr_prec.tif')
km_result <- raster('./km_segmentation_MT_yr_prec.tif')

pallete <- brewer.pal(6, 'Spectral')
par(mfrow=c(1,2))
plot(rf_result, col = pallete, main = 'randomForest')
plot(km_result, col = pallete,main = 'Kmeans')
```

##Running the segmentation with both algorithms

```{r, eval=FALSE, echo = TRUE, message = FALSE, warning = FALSE, results = 'hide'}
segmentation(envLayer = MT_prec, #raster Layer or raster stack
  studyArea = MT, # SpatialPolygonsDataFrame
  randomforest = TRUE,
  projName = 'MT_yr_prec',
  random.pt = NULL, # Number of random points to be genarated to run randomForest
  Kmeans = TRUE,
  ngroup = 100, # Number of classes to be classified
  polygonize = FALSE)
```